### 2014-04-04 paper/designspace.tex
clean up writing, re-add ryan text

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/types.png}
\caption{Pipe openings: A shows a pair of open tubes filled with copper paint to power an LED.  B shows a return pipe with EL wire threaded through it.  C shows two semi-closed pipes capped by rubber membranes.  In D, a rabbit has a fully enclosed chamber to modify its weight. \bjoern{Great, but make figure  full column wide}}
\label{fig:openings}
\end{figure}

@@

\subsection{Media in Pipes}
\tovi{clean up this writing}
One of the most interesting aspects of the design space is that pipes can be filled with a variety of media to create different interface affordances and capabilities. We consider gas, liquids, solids, particulates, and threadables.

@@

Threadable media, such as EL wire or fiberoptic cables, are those that can be threaded through pipes post-printing.  This empowers inexpensive printers: for example, a Printed Optics-style interface can be created on a consumer-grade 3D printer with pipes and fiber optic cable.

>>>>

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/types.png}
\caption{Pipe openings: A shows a pair of open tubes filled with copper paint to power an LED.  B shows a return pipe with EL wire threaded through it.  C shows two semi-closed pipes capped by rubber membranes.  In D, a rabbit has a fully enclosed chamber to modify its weight.}
\label{fig:openings}
\end{figure}

@@

\subsection{Media in Pipes}
After printing, there is still flexibility in inserting media to create different interface affordances and capabilities. We consider gas, liquids, solids, particulates, and threadables.

@@

Threadable media, such as EL wire or fiberoptic cables, can be threaded through pipes post-printing.  This empowers inexpensive printers: for example, a Printed Optics-style interface can be created on a consumer-grade 3D printer with pipes and fiber optic cable.

### 2014-04-04 paper/exampleobjects.tex
mmodz
photoshopize photos for nicer-ness
clean up writing, re-add ryan text

\begin{figure*}
\centering
    \includegraphics[width=7in]{figures/examples.png}
\caption{A series of example objects created using our system.  A) shows a portable radio.  B) shows a presence-aware pen holder.  C) is a rabbit which ``breathes'' using wind pipes we built.  D) shows a maze game we created.  E) is a touch-sensitive brain toy.  \valkyrie{finalize order of example objects.  what order is best?}}
\label{fig:examples}
\end{figure*}

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/sign.png}
\caption{A two-state animated neon sign designed using our tool (a)(b) \valkyrie{Tovi: we could use your PDF hax to make this animate in place :)}.  (c) shows the SVG input files to create this sign, and (d) shows an isometric view of the tubes created by our tool. \valkyrie{d) is a lot less interesting if we are making planar tubes.  also, for c, should we show an overlay of the two states?  maybe in different colors?}}
\label{fig:neon}
\end{figure}

>>>>

\begin{figure*}
\centering
    \includegraphics[width=7in]{figures/examples.png}
\caption{A series of example objects created using our system.  (a) is a touch-sensitive brain toy.  (b) is a rabbit which ``breathes'' using wind pipes we built.  (c) shows a portable radio.  (d) shows a presence-aware pen holder.  (e) is a maze game.}
\label{fig:examples}
\end{figure*}

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/sign.png}
\caption{A two-state animated neon sign designed using our tool.  (a) shows the input SVG files, with the two states of the mouth drawn in different colors.  (b) shows the resultant mesh when we subtracted the generated tubes.  In (c), we show the completed sign.}
\label{fig:neon}
\end{figure}

### 2014-04-04 paper/tubes.tex
paper modifications, and new figures!
clean up writing, re-add ryan text

Our A* pathfinding produces the \emph{shortest} path, but in many cases
we require a smoother path through which we can actually push a physical wire.
We solve this problem via physical simulation. We create a straight virtual 
wire (a 3D poly-line or \emph{discrete rod}), and then set its initial position 
to be deformed to lie along our A* path.
Running the physical simulation allows the wire to attempt to return to
its straight configuration, while satisfying endpoint position constraints.
We also increase the length of the wire, to provide some slack in cases where 
it would otherwise bend sharply to stay inside the shape.

The wire is modelled as a \emph{discrete rod}, ie a 3D poly-line with a bending 
constraint between adjacent segments. Our simulation is based on an
implementation of Position-Based Dynamics \cite{Muller07}, with all constraints
modelled as penalty forces. To keep the rod inside the
mesh, we compute a discretized distance field, we can then constrain the
rod to stay within some offset shell, again using a simple penalty force.
In the case of multiple initial paths, we solve for each smoothed path sequentially.
After solving for a path, we add it as a constraint to the system, generating
a penalty force that pushes additional paths away from it.

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/interior.png}
\caption{An input vector graphics file with the points which cannot be tubed as drawn highlighted in {\color{blue}blue} and the start and end points highlighted in {\color{gray}gray} (a).  The connected graph created by our software (b) and the resulting Euler circuit (c) permit creation of a novel neon sign (d).}
\label{fig:tool-process-interior}
\end{figure}

@@

Once we have a semi-Eulerian graph, we need to create an Euler tour.  We use a weighted modification of Fleury's algorithm for finding Euler tours\footnote{\url{http://en.wikipedia.org/wiki/Eulerian_path\#Fleury.27s_algorithm}} for this.  In the classic algorithm, each selected edge is removed to create a reduced graph.  To select the next edge while at a node, the algorithm randomly chooses from all incident non-bridge edges (where a bridge edge would create disconnected non-trivial subgraphs if it were removed).  This ensures that every edge is both reachable and traversed.  In our modification, instead of randomly selecting from non-bridge paths at each node, we select the non-bridge edge which turns the least from the most recent path (i.e., we prefer to pass straight through a node, if possible).  This minimizes turns in the final artifact, which eases support material removal and assembly.

@@

\subsection{Mesh Modification}

Once we have a set of authored paths, we must cut tubes out of the input mesh.
Our basic strategy is to create a polygonal tube by sweeping a profile polyline
along the path, and subtract the tube from the mesh. We only use circular profiles
in our examples, but clearly any other profile could be used. Similarly our interface
allows different start and end radii, which are linearly interpolated along the path.

To avoid the complexities of direct mesh booleans, we construct a discretized volumetric
(ie voxel-based) representation of the original mesh and the tube mesh. Boolean
subtraction is trivial in such representations. We specifically use narrow-band
level sets~\cite{Museth04}, which represent the surface as the zero iso-contour of an
approximate distance field.
We then use marching cubes~\cite{Lorensen87} to produce the final mesh for printing.
This strategy does incur some resampling artifacts, however so does the 3D printing, and compared to the print process, the time required to voxelize at high resolution is inconsequential.
Since we have a distance field, we can easily introduce useful effects, such as the
ability to add a thin membrane "cap" over the end of a tube. 
This is accomplished by applying a standard "thicken" operation to the level set version
of the initial mesh, intersecting with a sphere placed at the tube endpoint, and then performing
a boolean union with the initial shape-minus-tube result (see Figure \ref{fig:cap}).
A straightforward extension would be to add or subtract additional elements at
the tube endpoints to make them non-round.
 \ryan{Figure 8 is not necessary. This is a known problem with any voxelization method. Nobody is going to care that we took shortcuts in our implementation like repeatedly voxelizing and meshing instead of updating a single initial voxelization.}

>>>>

Our A* pathfinding produces the \emph{shortest} path, but in many cases
we require a smoother path through which we can actually push a physical wire.
We solve this problem via physical simulation. We create a straight virtual 
wire (a 3D poly-line or \emph{discrete rod}), and then set its initial position 
as our A* path.
Running the physical simulation allows the wire to attempt to return to
a straight configuration, while satisfying its endpoint position constraints.
We also increase the length of the wire, to provide some slack in cases where 
it would otherwise bend sharply to stay inside the shape.

The wire is modelled as a \emph{discrete rod}, i.e., a 3D poly-line with a bending 
constraint between adjacent segments. Our simulation is based on an
implementation of Position-Based Dynamics \cite{Muller07}, with all constraints
modelled as penalty forces. To keep the rod inside the
mesh, we compute a discretized distance field, we can then constrain the
rod to stay within some offset shell, again using a simple penalty force.
In the case of multiple initial paths, we solve for each smoothed path sequentially.
After solving for a path, we add it as a constraint to the system, generating
a penalty force that pushes additional paths away from it.

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/interior.pdf}
\caption{An input vector graphics file with the points which cannot be tubed as drawn highlighted in {\color{blue}blue} and the start and end points highlighted in {\color{gray}gray} (a).  The connected graph created by our software (b) and the resulting Euler circuit (c) permit creation of a novel neon sign (d).}
\label{fig:tool-process-interior}
\end{figure}

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/uistphotos.png}
\caption{Our neon sign built using the process above.  (a) shows the unlit sign, and (b) shows it lit.}
\label{fig:UIST}
\end{figure}

@@

Once we have a semi-Eulerian graph, we need to create an Euler tour.  We use a weighted modification of Fleury's algorithm for finding Euler tours\footnote{\url{http://en.wikipedia.org/wiki/Eulerian_path\#Fleury.27s_algorithm}} for this.  In the classic algorithm, each selected edge is removed to create a reduced graph.  To select the next edge while at a node, the algorithm randomly chooses from all incident non-bridge edges (where a bridge edge would create disconnected non-trivial subgraphs if it were removed).  This ensures that every edge is both reachable and traversed.  In our modification, instead of randomly selecting from non-bridge paths at each node, we select the non-bridge edge which turns the least from the most recent path (i.e., we prefer to pass straight through a node, if possible).  This minimizes turns in the final artifact, which eases support material removal and assembly.  Our EL wire in Figure \ref{fig:UIST} follows an Euler tour through the input nodes.

@@

\subsection{Mesh Modification}
Once we have a set of authored paths, we must cut tubes out of the input mesh.
Our basic strategy is to create a polygonal tube by sweeping a profile polyline
along the path, and subtract the tube from the mesh. We only use circular profiles
in our examples, but clearly any other profile could be used. Similarly our interface
allows different start and end radii, which are linearly interpolated along the path.

To avoid the complexities of direct mesh booleans, we construct a discretized volumetric
(i.e., voxel-based) representation of the original mesh and the tube mesh. Boolean
subtraction is trivial in such representations. We specifically use narrow-band
level sets~\cite{Museth04}, which represent the surface as the zero iso-contour of an
approximate distance field.
We then use marching cubes~\cite{Lorensen87} to produce the final mesh for printing.
This strategy does incur some resampling artifacts, however so does the 3D printing, and compared to the print process, the time required to voxelize at high resolution is inconsequential.
Since we have a distance field, we can easily introduce useful effects, such as the
ability to add a thin membrane ``cap'' over the end of a tube. 
This is accomplished by applying a standard ``thicken'' operation to the level set version
of the initial mesh, intersecting with a sphere placed at the tube endpoint, and then performing
a boolean union with the initial shape-minus-tube result (see Figure \ref{fig:cap}).
A straightforward extension would be to add or subtract additional elements at
the tube endpoints.
